\chapter{Introduction}
Disclaimer: J. K. Rowling owns Harry Potter, and no one owns the methods of
rationality.

This fic is widely considered to have really hit its stride starting at around
Chapter~5. If you still don't like it after Chapter~10, give up.

\SmallVSpace
Please visit HPMOR DOT COM for:

\SmallVSpace
\begin{itemize}
    \item Easy email notification system, RSS feed, and Twitter feed for new chapters;
    \item Current Author's Notes and progress updates;
    \item Lovely fan-made book-style PDF version;
    \item Ad-free mirror of the text;
    \item ePUB and MOBI e-texts;
    \item Ongoing podcast of the story;
    \item Fan art in vast quantities;
    \item Cameo list (characters named after fan artists);
    \item Fan-fanfiction of this fanfiction;
    \item Fan music, songs, and animations;
    \item Fan translations;
    \item The OKCupid keyword for HPMOR readers;
    \item Links to TV Tropes page and discussion forum;
    \item Trigger warnings page (warnings about possible traumatic associations
        for some readers; to avoid spoilers for most readers, there are
        \emph{no} warnings inside the main story);
    \item How to learn everything the main character knows;
    \item Open job positions at a related nonprofit;
    \item And ever so much more.
\end{itemize}

\SmallVSpace
Reviews make me happy. You can leave reviews on any chapter, no login required,
and there's no need to finish reading it all before you start reviewing
chapters---but do please leave at most \emph{one} review per chapter.

This is \emph{not} a strict single-point-of-departure fic---there exists a
primary point of departure, at some point in the past, but also other
alterations. The best term I've heard for this fic is "parallel universe".

The text contains many clues: obvious clues, not-so-obvious clues, truly
obscure hints which I was shocked to see some readers successfully decode, and
massive evidence left out in plain sight. This is a rationalist story; its
mysteries are solvable, and meant to be solved.

The pacing of the story is that of serial fiction, i.e., that of a TV show
running for a predetermined number of seasons, whose episodes are individually
plotted but with an overall arc building to a final conclusion.

The story has been corrected to British English up to Ch.~17, and further
Britpicking is currently in progress (see the /HPMOR
subreddit).\footnote{\emph{Editor's note:} Britpicking was never completed, and
    was undone in this edition; see the \emph{Note on the Text} on page
    \pageref{britpick note}.}

All science mentioned is real science. But please keep in mind that, beyond the
realm of science, the views of the characters may not be those of the author.
Not everything the protagonist does is a lesson in wisdom, and advice offered
by darker characters may be untrustworthy or dangerously double-edged.
