\thispagestyle{empty}
{
    \small
    \parindent=0pt
    \begin{center}
        \emph{Something, somewhere, somewhen, must have happened
        differently\el}
    \end{center}

    \MakeUppercase{Petunia Evans} married Michael Verres, a Professor of
    Biochemistry at Oxford.

    \bigskip
    \MakeUppercase{Harry James Potter-Evans-Verres} grew up in a house filled
    to the brim with books. He once bit a math teacher who didn't know what a
    logarithm was.  He's read Godel, Escher, Bach and Judgment Under
    Uncertainty: Heuristics and Biases and volume one of The Feynman Lectures
    on Physics. And despite what everyone who's met him seems to fear, he
    doesn't want to become the next Dark Lord. He was raised better than that.
    He wants to discover the laws of magic and become a god.

    \bigskip
    \MakeUppercase{Hermione Granger} is doing better than him in every class
    except broomstick riding.

    \bigskip
    \MakeUppercase{Draco Malfoy} is exactly what you would expect an
    eleven-year-old boy to be like if Darth Vader were his doting father.

    \bigskip
    \MakeUppercase{Professor Quirrell} is living his lifelong dream of teaching
    Defense Against the Dark Arts, or as he prefers to call his class, Battle
    Magic. His students are all wondering what's going to go wrong with the
    Defense Professor this time.

    \bigskip
    \MakeUppercase{Dumbledore} is either insane, or playing some vastly deeper
    game which involved setting fire to a chicken.

    \bigskip
    \MakeUppercase{Deputy Headmistress Minerva Mcgonagall} needs to go off
    somewhere private and scream for a while.

    \begin{center}
        Presenting:

        \bigskip
        \MakeUppercase{Harry Potter and the Methods of Rationality}

        \bigskip
        You ain't guessin' where this one's going.
    \end{center}
}
