\input{hp-header}

\begin{document}
\frontmatter
\newcommand{\hpBookNo}{1}
\newcommand{\hpBookChar}{Harry James Potter-Evans-Verres}
\newcommand{\hpBookTitle}{Methods of Rationality}
\input{hp-titlepage}
\input{hp-contents}
\cleartorecto
\chapter{Note on the Text}
This story was originally published chapter by chapter on the website
\href{https://www.fanfiction.net/s/5782108/1/Harry-Potter-and-the-Methods-of-Rationality}{\UrlFont fanfiction.net}.
In preparing the present edition, a few decisions were made to balance
conflicting interests: preserving the character of the fan fiction as it was
published, and adapting the text to a form more appropriate for a printed book.

The text is divided in six books, as was suggested by the author, who also
provided the book titles. As a service to the reader who might want to research
or discuss the material on internet, it was deemed preferable to keep the
original chapter numbering, so that book 2 starts at chapter 22, book 3 at
chapter 38 and so on.

The fan fiction as published on the Web includes material that is not part of
the story. Chapters 11 and 64 are \emph{omake}, i.e.\ bonus for the fans. These
were kept in the present edition. The \emph{final exam} section of chapter 113,
a challenge addressed to the reader, is also included. On the other hand, the
epigraphs at the beginning of the early chapters, most of the author's notes,
and the reminders on the Harry Potter copyright were left out.

\label{britpick note}Following their publication online, chapters 1--17 were subjected to
\emph{Britpicks}. This is a procedure commonly applied to American fan fiction
of British books, in which native British speakers correct the text to better
conform it to the language and culture of its setting. Since only 17 chapters
out of 122 were corrected, an attempt was made here to undo the Britpicks for
increased consistency throughout the text.

\include{hp-intro}
\addtocontents{toc}{\vspace{7pt}}% Add some space between front- and main-matter in TOC
\clearpage
\thispagestyle{empty}
\begin{vplace}[.27]
    \itshape
    \parindent=0pt\small
    Beneath the moonlight glints a tiny fragment of silver, a fraction of a line{\el}

    \medskip
    (black robes, falling)

    \medskip
    {\el} blood spills out in litres, and someone screams a word.
\end{vplace}
\mainmatter
\include{chapters/hpmor-chapter-001}
\include{chapters/hpmor-chapter-002}
\include{chapters/hpmor-chapter-003}
\include{chapters/hpmor-chapter-004}
\include{chapters/hpmor-chapter-005}
\include{chapters/hpmor-chapter-006}
\include{chapters/hpmor-chapter-007}
\include{chapters/hpmor-chapter-008}
\include{chapters/hpmor-chapter-009}
\include{chapters/hpmor-chapter-010}
\include{chapters/hpmor-chapter-011}
\include{chapters/hpmor-chapter-012}
\include{chapters/hpmor-chapter-013}
\include{chapters/hpmor-chapter-014}
\include{chapters/hpmor-chapter-015}
\include{chapters/hpmor-chapter-016}
\include{chapters/hpmor-chapter-017}
\include{chapters/hpmor-chapter-018}
\include{chapters/hpmor-chapter-019}
\include{chapters/hpmor-chapter-020}
\include{chapters/hpmor-chapter-021}

\include{hp-colophon}
\end{document}
